\mytitle

### 2015-08-04 MSc_diss.tex
Finished draft of literature review and introduction

\section{Literature review} \label{sec:lit_review}
A lot of work is has been dedicated to measurements of alkyl nitrates in different environments and even more to measurements of ozone. The majority of these studies have been done in a observational-modelling framework.

During/After one of these investigations, namely the SAGA campaign, \citep{Atlas1993} first postulated that the short-chained alkyl nitrates ($C_1$-$C_3$) can be produced not only photochemically through the oxidation of their parent hydrocarbons \citep{Roberts1990}, but also emitted directly from equatorial oceans. This has since been confirmed by field measurements \citep{Chuck2002,Blake2003,Dahl2005}. \citep{Chuck2002} provided the first direct evidence of that based on detection of supersaturation of surface waters by methyl and ethyl nitrates and their high concentrations in the marine air over equatorial areas (0-40$^{\circ}$) of the Atlantic. Later during two extensive NASA airborne campaigns Pacific Exploratory Mission (PEM)-Tropics A (September-October 1996) and PEM-Tropics B (March-April 1999) \citep{Blake2003} observed high levels of methyl and ethyl nitrates (approximately 50 ppt) in the air at the band between 8$^{\circ}$N-13$^{\circ}$S stretching across the equatorial Pacific, and pointed out that oceanic source of $\geq C_4$ alkyl nitrates is insignificant compared to anthropogenic sources.

@@

There have been a number of studies of the seasonal variations of alkyl nitrates in the Arctic \citep{Swanson2003} and in the Antarctic \citep{Beyersdorf2010}. Polar alkyl nitrate follow the seasonality of the alkanes displaying a clear late winter maximum and a broad summer minimum.

@@

\subsubsection*{Continent}
\citep{Day2003}
We describe measurements of NO2, total peroxy nitrates (?PNs), total alkyl nitrates (?ANs), and HNO3 using thermal dissociation followed by laser-induced fluorescence detection of NO2 at three continental locations. At a rural site in California, measurements over a full annual cycle show that ?ANs are routinely 10–20\% of NOy. rural site, at a suburban site in California and an urban site in Houston, Texas [rural (UC-BFRS), suburban (Granite Bay) and urban (La Porte)]
SumANs a more broad term than usual.
?AN mixing ratios at the UC-BFRS exhibit a strong seasonal cycle with a minimum in winter and a maximum in summer. The seasonal transition is sharp. Concentrations of ?ANs rise rapidly from 150 ppt at the end of April to 500 ppt by early June.
We also show that ?ANs are a large part, if not all, of the ‘‘missing NOy’’.

\citep{Simpson2006} Pearl River Delta
Mixing ratios of seven C1–C5 alkyl nitrates (RONO2) were measured during a 16-month study (August 2001–December
2002) at Tai O, a coastal site 30km west of central Hong Kong in the Pearl River Delta, the fastest-growing industrial region in the world. The C3–C4 (rather than C1–C2) RONO2 were most abundant throughout the study, showing the importance of photochemical (rather than marine) RONO2 production in the sampled air. A lack of methyl nitrate (MeONO2) enhancement during summer, when the prevailing winds are from the ocean, indicates that the South China Sea is not a region of strong RONO2 emissions. By contrast, MeONO2 levels during pollution episodes (up to 25 parts per trillion by volume (pptv)) were the highest that our group has recorded during urban photochemical RONO2 production, as opposed to marine emissions or biomass burning. The highest summed RONO2 level of the study (204 pptv) was measured in the afternoon of 7 November 2002, during an intense pollution episode that captured the highest ozone (O3) level ever recorded in Hong Kong (203 ppbv). During pollution episodes, the average ratio of O3 to summed RONO2 was
roughly 1000:1 in freshly polluted air (ethyne/CO?3–5 pptv/ppbv) and 500:1 in very freshly polluted air (ethyne/ CO?6–8 pptv/ppbv). Ozone and RONO2 share a common photochemical source, and their good correlation in pollution plumes shows that RONO2 can be used as a tracer of photochemical O3 production. Even MeONO2 showed similar
diurnal variations as the C2–C5 RONO2, indicating a strong photochemical source despite its very slow photochemical production from methane oxidation. The decomposition of longer-chain alkoxy radicals also does not explain the high MeONO2 levels, and rough calculations show that methoxy radical reaction with NO2 appears to be a viable alternate pathway for MeONO2 production in polluted atmospheres, though further measurements and modeling are required to confirm this mechanism.
\citep{Comment}
It has generally been assumed that reaction (3) dominates over reaction (2) and that production of CH3ONO2 would be small. Simpson et al. (2006) suggest that model studies would be useful to test their theory. In this short comment on their paper, some model simulations are presented that confirm their hypothesis.The model simulations have been carried out using a box model running the CRI v1.0 mechanism (Jenkin et al., 2002), which is a reduced scheme of the Master Chemical Mechanism (Jenkin et al., 1997). The box model was integrated using emissions of NOx and VOC taken from the UK National emissions inventory and would be repre- sentative therefore of European rather than Asian emission profiles but are still instructive. The model is designed to simulate regional photochemical episodes and runs during European summer time (mid June) under moderately high temperature (approximately 25 1C) and relative humidity (70\%). The concentration of CH3ONO2 from the two routes, reaction (1b) and reaction (2), have been compared as a function of NOx and are summarised in Fig. 1. It is clear that above about 10 ppb of NO2 channel (2) becomes important as a source of CH3ONO2 and at around 35 ppb starts to become the dominant channel in the simulations performed.

\citep{deKock1994}
Air samples were collected at Cape Recife (34 1' S 25 40'E) situated on the south-east coast of Southern Afirica (Figure 1). The suburban, urban and industrial areas of Port Elizabeth lie approximately 10-40 kin north to north-west of the sampling site.
Mean sumANs 12.7.
Variations in absolute and relative concentrations of the alkyl nitrates could be related to changes in meteorological conditions. It is considered that the differences observed in chemical composition may represent different sources of trace gas emissions or different degrees of photochemical processing of similar sources. The meas~ed levels of the alkyl nitrates suggest long-range transport to play a major role in regulating the distribution of alkyl nitrates in the troposphere.

\subsubsection*{Oceanic sources}
\citep{Reeves2007} ocean+urban+fire
This paper is based on alkyl nitrate measurements made over the North Atlantic as part of the International Consortium for Research on Atmospheric Transport and Transformation (ICARTT). The focus is on the analysis of air samples collected on the UK BAe-146 aircraft during the Intercontinental Transport of Ozone and Precursors (ITOP) project, but air samples collected on board the NASA DC-8 and NOAA WP-3D aircraft as part of a Lagrangian experiment are also used. The ratios between the alkyl nitrates and their parent hydrocarbons are compared with those expected from chemical theory. Further, a box model is run to investigate the temporal evolution of the alkyl nitrates in three Lagrangian case studies and compared to observations.
The general agreement between the alkyl nitrate data and photochemical theory suggests that during the first few days of transport from the source region, photochemical production of alkyl nitrates, and thus ozone, had taken place.
Concentrations of methyl, ethyl, 1-propyl, 2-propyl, 2-butyl, 2-methyl-3-butyl and the sum of 2- and 3-pentyl nitrates (hereafter referred to as 2 + 3-pentyl nitrate) are presented.
The alkyl nitrate concentrations observed during
ITOP are typical of those found a few days downwind of precursor source regions. Although there is some evidence for an oceanic source of methyl nitrate, for the most part the air samples collected during ITOP do not appear to be strongly influenced by oceanic sources of the alkyl nitrates. Elevated concentrations were observed in air masses which have been influenced by emissions from the N.E. United States and from Alaskan fires. The large variations in ratios between the C5 and C2-C4 nitrates suggest that emission ratios for the parent hydrocarbons vary between different regions of the N.E. United States. [49] In general the alkyl nitrate data agrees well with photochemical theory. This suggests that at least during the first few days of transport from the source region photo- chemical production of alkyl nitrates had taken place. This implies that ozone production had also occurred. There also appears to be a widespread common source of ethyl nitrate and 1-propyl nitrate other than from their parent hydro- carbons. This might be from longer-chain hydrocarbons, possibly pentanes. [50] The observations in the more photochemically pro- cessed air masses are consistent with the concentration of NO dropping to a point where the rates of the alkyl nitrate production reactions no longer dominate the peroxy radical self/cross reactions. However, in these low levels of NO, where the balance between ozone production and destruc- tion is highly sensitive to NOX, the alkyl nitrates might contribute to maintaining the ozone levels in air as it undergoes long-range transport. [51] The observed patterns of the alkyl nitrates also suggest that the rates of photochemical processing in the Alaskan smoke plumes were small and that the rates of ozone formation in these air masses were low.

\begin{table}%[ht] % mean AN mixing ratios
\begin{tabular}{cccc}
\hline
Environment     & Mean $\Sigma RONO_2$ & $\Sigma RONO_2$ breakdown & Reference \\
\hline
remote marine   & 10 pptv    & methyl                   & \citep{Reeves2007} \\
(North Atlantic)&            & ethyl                    & \\
airborne        &            & 1-propyl                 & \\   
                             && 2-propyl                & \\   
                             && 2-butyl                 & \\                                                                                               
                             && 2-methyl-3-butyl        & \\
                             && sum of 2- and 3-pentyl  & \\
\hline
rural           & 14 pptv    & methyl                   & \citep{Roberts1998} \\
(Nova Scotia, Canada)        &&  ethyl   & \\
stationary                   && n-propyl & \\
Chebogue Point               && 2-propyl & \\
                             && 2-butyl  & \\ 
\hline
rural         & 120 ppt (30-630 ppt) & $C_1$-$C_8$       & \citep{Flocke1998} \\
(Black Forest, Germany)      &&& \\ 
stationary                   &&& \\
\hline
polluted marine & approx 1 ppb        & $NO_y$-($NO_x$+$HNO_3$+$PAN$) & \citep{Neuman2012} \\
(Gulf of Mexico)&(plume center) && \\
airborne &&& \\
\hline
\end{tabular}
\end{table}
%??                         & MeONO2: 1.2 to 43 pptv     &          & \citep{Chuck2002} \\
%??                         & EtONO2: 0.8 to 10 pptv     &          & \citep{Chuck2002} \\
%remote marine & MeONO2: 0.2 to 50 pptv     & in lit. (2, 8, 9) & \citep{Chuck2002} \\
%remote marine & EtONO2: 0.3 to 12.2 pptv   & in lit. (2, 8, 9) & \citep{Chuck2002} \\
%Pacific Ocean & MeONO2: 50 pptv            &                   & \citep{Blake2003} \\

\subsubsection*{Comparison methodology}
\citep{Sommariva2008}
[The ratios between the alkyl nitrates and their
main alkane precursors can also be plotted against one another, for example against 2-butylnitrate/ n-butane as in Fig. 4. In this way the modelled and the measured concentrations can be compared without taking into account their variation with time. A similar approach was used in previous studies to investigate the sources of alkyl nitrates and the photochemical processing of polluted air masses (e.g., Bertman et al., 1995; Flocke et al., 1998; Roberts et al., 1998; Stroud et al., 2001; Simpson et al., 2003; Reeves et al., 2007). These studies compared plots of the measured ratios against 2-butylnitrate/n-butane to the ratios calculated with a simple sequential reaction model which assumed a single precursors for each alkyl nitrate. Usually, the underestimation of the ratios for short- chain compounds (propylnitrates/propane, ethylni- trate/ethane) was interpreted as an indication of photochemical sources other than the main alkane precursor.]

\citep{Day2003}
We also show that sumANs are a large part, if not all, of the 'missing NOy' reported in many prior experiments and emphasize that the ratios of sumANs/NOz and of O3/sumANs are especially useful for evaluating chemical models and comparing observations at different sites.

\subsubsection*{Modelling studies}
A huge number of modelling studies has been done about alkyl nitrates. In particular, O3 and the RONO2 oxidation products formed from reactions between these NOx and VOC emissions are examined in detail...

@@

\begin{figure}[h!]\label{fig:Neuman2012}
\includegraphics[width=.5\linewidth]{{D:/UEA/ENV-MB4X_Dissertation/ENV-MB4X_Dissertation_thesis/ENV-MB4X_Dissertation_thesis_latex/pics/Neuman2012_Fig.4}.png}
\caption{Time series of reactive nitrogen species measured on 10 June 2010 in the MBL in plumes (a) 10 km and (b) 50 km downwind from DWH. $NO_x$, $NO_y$, and $HNO_3$ were measured once per s and $PAN$ was measured once per 2 s. $C_1$–$C_5$ alkyl nitrates were measured in whole air samples at locations indicated by the circles. The sum of alkyl nitrates (black lines) is inferred from the difference between $NO_y$ and ($NO_x$+$HNO_3$+$PAN$) \citep{Neuman2012}.}
\end{figure}

@@

\begin{table}\label{tab:Sommariva2008init}
\caption{Initial values of the some model parameters (in ppb) for two scenarios used in \citep{Sommariva2008}}
\begin{tabular}{ccc}
\hline
Parameter & Initial value Scenario A & Scenario B \\
\hline
$CO$      & 332.5 & 232.5 \\
$NO_x$    & 34.9  & 46.5  \\
$O_3$     & 90    & 0   \\
\hline
\end{tabular}
\end{table}
\begin{figure}\label{fig:Sommariva2008fig}
\includegraphics[width=\linewidth]{{D:/UEA/ENV-MB4X_Dissertation/ENV-MB4X_Dissertation_thesis/ENV-MB4X_Dissertation_thesis_latex/pics/Sommariva2008_Fig.1}.png}
\caption{Modelled concentrations of $O_3$, $NO_x$ and $HNO_3$ for scenario A (left) and B (right). Source: \citep{Sommariva2008}.}
\end{figure}

\subsubsection*{Other}

@@

Using methyl nitrate as a tracer of marine $RONO_2$ \cite{Simpson2006} revealed that the South China Sea in not a region of strong $RONO_2$ emissions suggesting that photochemical rather marine production of alkyl nitrates is dominant at the site.

@@

The best way to illustrate the central features of the relationship between $O_3$, $NO_x$ and $VOC$ mentioned above is to construct a ozone isopleth plot in a form shown in Figure \ref{fig:Sillman1999}. The isopleth plot shows that the rate of $O_3$ production is a nonlinear function of the $NO_x$ and $VOC$ concentrations. When $VOC$/$NO_x$ ratios are high, the $O_3$ production rate increases with increasing $NO_x$ eventually reaching a local maximum, and decreasing afterwards as $NO_x$ concentrations continue to increase. The local maximum (the 'ridge line') defines the split into $NO_x$-sensitive and $VOC$-sensitive regimes. Under the 'ridge line' the $VOC$/$NO_x$ ratios are high, and the $O_3$ production rate increases with increasing $NO_x$ and almost insensitive to $VOC$. Above the 'ridge line' the $VOC$/$NO_x$ ratios are low, and the $O_3$ production rate increases with increasing $VOC$ and decreases with increasing $NO_x$ \citep{Sillman2013}.

\begin{figure} % Sillman1999withdotsline and netO3rate_withINORG_NOx_1ppb_100ppb
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotsrectangle}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_NOx_1ppb_100ppb.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3rate}
\end{minipage}
\end{figure}

Rewrite!

@@

As it has been noted in Section \ref{sec:intro}, the relationship between $O_3$ and $RONO_2$ production rates is controlled by the branching ratio ($\alpha_3$) between reactions:
\begin{equation}\label{reac:RO2+NO=RO+NO2}
RO_2 + NO \xrightarrow{1-\alpha_3} RO + NO_2
\end{equation}
\begin{equation}\label{reac:RO2+NO=RONO2}
RO_2 + NO \xrightarrow{\alpha_3} RONO_2
\end{equation}
Reaction (\ref{reac:RO2+NO=RO+NO2}) leads to $O_3$ production and $NO$ regeneration, resulting in continuing $O_3$ production, while reaction (\ref{reac:RO2+NO=RONO2}) terminates this process. Branching ratios used in the model are taken from the MCM v3.3, and their values (Table \ref{tab:ANbranching}) were kept constant in all model runs.

\begin{table} %  AN branching ratios
\caption{Branching ratios for the formation of alkyl nitrates from their precursor peroxy radicals and $NO$ (taken from the MCM v3.3 (2015)).}\label{tab:ANbranching}
\centering
\begin{tabular}{cc}
\hline
Alkyl nitrate    & Branching ratio \\
\hline
methyl           & 0.001 \\
ethyl            & 0.009 \\
iso-propyl       & 0.042 \\
n-propyl         & 0.020 \\
n-butyl          & 0.033 \\
sec-butyl        & 0.090 \\
iso-butyl        & 0.033 \\ 
tert-butyl       & 0.025 \\
n-pentyl         & 0.052 \\
2-pentyl         & 0.129 \\
3-pentyl         & 0.131 \\
2-methylbutyl    & 0.052 \\
3-methyl-2-butyl & 0.141 \\
2-methyl-2-butyl & 0.047 \\
\hline
\end{tabular}
\end{table}

Figure \ref{fig:netO3rate_noAN_withAN_diff} shows isopleths of net $O_3$ production rate as a function of $NO_x$ and sum of $VOCs$ initial concentrations from two series of model runs (with and without alkyl chemistry) and the difference between them. Since the actual formation of $O_3$ in our model starts at 250 ppt of $NO_x$, Figure \ref{fig:netO3rate_noAN_withAN_diff} summarises modelling data from experiments with $NO_x$ initial mixing ratios from 250 ppt till 100 ppb.

\begin{figure} % netO3rate noAN withAN diff
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3ratediff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:netO3rate_noAN_withAN_diff}
\end{figure}

As expected, the inclusion of alkyl nitrate chemistry slows down the net $O_3$ production rate. At low $NO_x$ and $VOCs$ initial levels, this slowdown is -0.2...-0.6 ppb of $O_3$ per hour. As $NO_x$ and $VOCs$ levels increase the $O_3$ production rate decreases, reaching the maximum decrease of -1.94 ppb of $O_3$ per hour at 100 ppb of $NO_x$ and $VOCs$ level from case I (not the highest $VOCs$ level). At the range of $NO_x$ levels from 1 ppb to 10 ppb the $O_3$ production rate is slightly more sensitive to $VOCs$ levels, while it is almost insensitive to $VOCs$ at $NO_x$ levels higher than 10 ppb and 2050 ppbC of $VOCs$.

@@

\citep{Reeves2007}
[In the 'marine' air masses methyl nitrate shows a slightly higher mean concentration to 'other' air masses (2.40 compared to 2.29 ppt), but the concentrations of the other alkyl
nitrates are lower by around 30–50% with the exception of
ethyl nitrate which is lower by about 15% (1.33 compared to
1.57 ppt), such that it becomes the second most abundant alkyl
nitrate.
The highest alkyl
nitrate concentration was observed during flight B031 (air
from New York) for 2-methyl-3-butyl nitrate (13.7 ppt),
when the maximum concentration of 2 + 3-pentyl nitrate
(9.0 ppt) was also measured. It is quite possible that some of
the ‘‘marine’’ maximum concentrations of the alkyl nitrates
were impacted by terrestrial emissions (e.g., 5.4 pptv of
2-methyl-3-butyl nitrate and 1.7 pptv for 2 + 3-pentyl nitrate
observed during flight B030).

The mean NO concentration observed during ITOP (20 plus minus 31 pptv (Lewis et al., 2007)) is below the limit of 100–200 pptv at which the efficiency of the alkyl nitrate formation is reduced because of competition between the reaction of ROO with NO and ROO self/cross reactions (Roberts et al., 1998)]

>>>>

\section{Literature review} \label{sec:lit_review}
A lot of work is has been dedicated to measurements of alkyl nitrates in different environments and even more to measurements of ozone. Here we focus our attention on some major investigations that lead us to our current understanding of the relationship between tropospheric ozone and alkyl nitrates.

During one of these investigations, namely the SAGA campaign, \citep{Atlas1993} first postulated that the short-chained alkyl nitrates ($C_1$-$C_3$) can be produced not only photochemically through the oxidation of their parent hydrocarbons \citep{Roberts1990}, but also emitted directly from equatorial oceans. This has since been confirmed by field measurements \citep{Chuck2002,Blake2003,Dahl2005}. \citep{Chuck2002} provided the first direct evidence of that based on detection of supersaturation of surface waters by methyl and ethyl nitrates and their high concentrations in the marine air over equatorial areas (0-40$^{\circ}$) of the Atlantic. Later during two extensive NASA airborne campaigns Pacific Exploratory Mission (PEM)-Tropics A (September-October 1996) and PEM-Tropics B (March-April 1999) \citep{Blake2003} observed high levels of methyl and ethyl nitrates (approximately 50 ppt) in the air at the band between 8$^{\circ}$N-13$^{\circ}$S stretching across the equatorial Pacific, and pointed out that oceanic source of $\geq C_4$ alkyl nitrates is insignificant compared to anthropogenic sources.

@@

There have been a number of studies of the seasonal variations of alkyl nitrates in the Arctic \citep{Swanson2003} and in the Antarctic \citep{Beyersdorf2010}. They show that polar alkyl nitrate follow the seasonality of the alkanes displaying a clear late winter maximum and a broad summer minimum. In temperate latitudes, seasonal variations of alkyl nitrate depend more on the origin of an air mass. In polluted air masses, the mixing ratios of alkyl nitrates exhibited summer maximum and strong daily variations, with maximum in the early evening. In clean air masses, alkyl nitrate mixing ratios showed a summer minimum and no pronounced diurnal variation \citep{Flocke1998}. Mean mixing ratios of the sum of alkyl nitrates measured in different environments can be found in Table \ref{tab:ANmean}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}\label{tab:ANmean} % mean AN mixing ratios
\begin{tabular}{cccc}
\hline
Environment     & Mean $\Sigma RONO_2$ & $\Sigma RONO_2$ breakdown & Reference \\
\hline
remote marine   & 10 pptv    & methyl                   & \citep{Reeves2007} \\
(North Atlantic)&            & ethyl                    & \\
airborne        &            & 1-propyl                 & \\   
                             && 2-propyl                & \\   
                             && 2-butyl                 & \\                                                                                               
                             && 2-methyl-3-butyl        & \\
                             && sum of 2- and 3-pentyl  & \\
\hline
rural           & 14 pptv    & methyl                   & \citep{Roberts1998} \\
(Nova Scotia, Canada)        && ethyl   & \\
ground                       && n-propyl & \\
                             && 2-propyl & \\
                             && 2-butyl  & \\ 
\hline
suburban                     & 17.48 pptv  & 2-propyl    & \citep{DeKock1994} \\
(Cape Retire, South Africa)  &(3.62-122.23)& 1-propyl & \\
ground                                    && 2-butyl  & \\
                                          && 1-butyl  & \\
                                          && 3-pentyl & \\
                                          && 2-pentyl & \\
                                          && 2-methyl-1-butyl & \\
                                          && i-pentyl & \\
\hline
suburban                     & 119.8 ppt  & $C_1$-$C_8$       & \citep{Flocke1998} \\
(Black Forest, Germany)      & (30-630 ppt) && \\ 
ground                                     &&& \\
\hline
polluted marine & approx 1 ppb & $NO_y$-($NO_x$+$HNO_3$+$PAN$) & \citep{Neuman2012} \\
(Gulf of Mexico)&(plume center) && \\
airborne &&& \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]\label{fig:Neuman2012}
\includegraphics[width=.5\linewidth]{{D:/UEA/ENV-MB4X_Dissertation/ENV-MB4X_Dissertation_thesis/ENV-MB4X_Dissertation_thesis_latex/pics/Neuman2012_Fig.4}.png}
\caption{Time series of reactive nitrogen species measured on 10 June 2010 in the MBL in plumes (a) 10 km and (b) 50 km downwind from DWH. $NO_x$, $NO_y$, and $HNO_3$ were measured once per s and $PAN$ was measured once per 2 s. $C_1$–$C_5$ alkyl nitrates were measured in whole air samples at locations indicated by the circles. The sum of alkyl nitrates (black lines) is inferred from the difference between $NO_y$ and ($NO_x$+$HNO_3$+$PAN$) \citep{Neuman2012}.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}\label{tab:Sommariva2008init}
\caption{Initial values of the some model parameters (in ppb) for two scenarios used in \citep{Sommariva2008}}
\begin{tabular}{ccc}
\hline
Parameter & Initial value Scenario A & Scenario B \\
\hline
$CO$      & 332.5 & 232.5 \\
$NO_x$    & 34.9  & 46.5  \\
$O_3$     & 90    & 0   \\
\hline
\end{tabular}
\end{table}
\begin{figure}\label{fig:Sommariva2008fig}
\includegraphics[width=\linewidth]{{D:/UEA/ENV-MB4X_Dissertation/ENV-MB4X_Dissertation_thesis/ENV-MB4X_Dissertation_thesis_latex/pics/Sommariva2008_Fig.1}.png}
\caption{Modelled concentrations of $O_3$, $NO_x$ and $HNO_3$ for scenario A (left) and B (right). Source: \citep{Sommariva2008}.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

The best way to illustrate the central features of the relationship between $O_3$, $NO_x$ and $VOC$ mentioned above is to construct a ozone isopleth plot in a form shown in Figure \ref{fig:Sillman1999}. The isopleth plot shows that the rate of $O_3$ production is a nonlinear function of the $NO_x$ and $VOC$ concentrations. When $VOC$/$NO_x$ ratios are high, the $O_3$ production rate increases with increasing $NO_x$ eventually reaching a local maximum, and decreasing afterwards as $NO_x$ concentrations continue to increase. The local maximum (the 'ridge line') defines the split into $NO_x$-sensitive and $VOC$-sensitive regimes. Under the 'ridge line' the $VOC$/$NO_x$ ratios are high, and the $O_3$ production rate increases with increasing $NO_x$ and almost insensitive to $VOC$. Above the 'ridge line' the $VOC$/$NO_x$ ratios are low, and the $O_3$ production rate increases with increasing $VOC$ and decreases with increasing $NO_x$ \citep{Sillman2013}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % Sillman1999withdotsline and netO3rate_withINORG_NOx_1ppb_100ppb
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotsrectangle}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_NOx_1ppb_100ppb.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3rate}
\end{minipage}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Rewrite!

@@

As it has been noted in Section \ref{sec:intro}, the relationship between $O_3$ and $RONO_2$ production rates is controlled by the branching ratio ($\alpha_3$) between reactions:
\begin{equation}\label{reac:RO2+NO=RO+NO2}
RO_2 + NO \xrightarrow{1-\alpha_3} RO + NO_2
\end{equation}
\begin{equation}\label{reac:RO2+NO=RONO2}
RO_2 + NO \xrightarrow{\alpha_3} RONO_2
\end{equation}
Reaction (\ref{reac:RO2+NO=RO+NO2}) leads to $O_3$ production and $NO$ regeneration, resulting in continuing $O_3$ production, while reaction (\ref{reac:RO2+NO=RONO2}) terminates this process. Branching ratios used in the model are taken from the MCM v3.3, and their values (Table \ref{tab:ANbranching}) were kept constant in all model runs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} %  AN branching ratios
\caption{Branching ratios for the formation of alkyl nitrates from their precursor peroxy radicals and $NO$ (taken from the MCM v3.3 (2015)).}\label{tab:ANbranching}
\centering
\begin{tabular}{cc}
\hline
Alkyl nitrate    & Branching ratio \\
\hline
methyl           & 0.001 \\
ethyl            & 0.009 \\
iso-propyl       & 0.042 \\
n-propyl         & 0.020 \\
n-butyl          & 0.033 \\
sec-butyl        & 0.090 \\
iso-butyl        & 0.033 \\ 
tert-butyl       & 0.025 \\
n-pentyl         & 0.052 \\
2-pentyl         & 0.129 \\
3-pentyl         & 0.131 \\
2-methylbutyl    & 0.052 \\
3-methyl-2-butyl & 0.141 \\
2-methyl-2-butyl & 0.047 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:netO3rate_noAN_withAN_diff} shows isopleths of net $O_3$ production rate as a function of $NO_x$ and sum of $VOCs$ initial concentrations from two series of model runs (with and without alkyl chemistry) and the difference between them. Since the actual formation of $O_3$ in our model starts at 250 ppt of $NO_x$, Figure \ref{fig:netO3rate_noAN_withAN_diff} summarises modelling data from experiments with $NO_x$ initial mixing ratios from 250 ppt till 100 ppb.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3rate noAN withAN diff
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3ratediff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:netO3rate_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
As expected, the inclusion of alkyl nitrate chemistry slows down the net $O_3$ production rate. At low $NO_x$ and $VOCs$ initial levels, this slowdown is -0.2...-0.6 ppb of $O_3$ per hour. As $NO_x$ and $VOCs$ levels increase the $O_3$ production rate decreases, reaching the maximum decrease of -1.94 ppb of $O_3$ per hour at 100 ppb of $NO_x$ and $VOCs$ level from case I (not the highest $VOCs$ level). At the range of $NO_x$ levels from 1 ppb to 10 ppb the $O_3$ production rate is slightly more sensitive to $VOCs$ levels, while it is almost insensitive to $VOCs$ at $NO_x$ levels higher than 10 ppb and 2050 ppbC of $VOCs$.

@@
